---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plausibler

<!-- badges: start -->
<!-- badges: end -->

`plausibler` is a wrapper for the R programming language to the [Plausible Analytics](https://plausible.io/) API. It facilitates making queries, and getting tidy data frames in return.

See the [Plausible Analytics API documentation](https://plausible.io/docs/stats-api) for more details on the API, the endpoints, etc.

## Installation

You can install `plausibler` from GitHub with:

``` r
remotes::install_github("giocomai/plausibler")
```

To facilitate interactive use and auto-complete, each function starts with "pa_" (for "Plausible Analytics") followed by a verb describing what the function does.

## Example

At the beginning of each session, you will need to set the base url of your Plausible Analytics instance (if not self-hosted, https://plausible.io/), your `site_id` (the domain of your website), and your API key. 

```{r, eval=FALSE}
pa_set(base_url = "https://plausible.io/",
       site_id = "example.com",
       key= "actual_key_here")
```


You have then three main options to get data from the API. 

If you know exactly your query, you can just go with it. You can e.g. see your monthly stats for the last six months with:

```{r, eval=FALSE}
pa_get(full_url = "https://plausible.io/api/v1/stats/timeseries?site_id=$SITE_ID&period=6mo")
```

Keep in mind that you will still need to set the key with `pa_set()`. Replace $SITE_ID with your domain in this example, or check out the [official API documentation](https://plausible.io/docs/stats-api) for many more examples.

If you prefer to stick to a syntax closer to what you would typically use in R, you can achieve the same as above with the following:

```{r, eval = FALSE}
pa_get(endpoint = "/api/v1/stats/timeseries",
       parameters = list(period = "6mo"))
```

Finally, you can use wrapper functions, so you don't need to remember the endpoint. Here are some example for time series data:

```{r, eval = FALSE}
pa_get_timeseries(period = "6mo")
pa_get_timeseries(period = "30d")
pa_get_timeseries(period = "custom&date=2021-06-01,2021-06-07")
```

## Future development

- more wrapper functions
- maybe, local caching with sqlite
- suggestions? Open an issue
